Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-02-21 pkg/disttree/inst/draft/draft.Rnw
semi-transparent qqrplot als PNG not PDF to save some space
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2032 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 94fb2867fd31d37aab65684837f91540d8ad028f

\begin{figure}[t!]
\centering
\setkeys{Gin}{width=0.99\textwidth}
<<rain_axams_qqr_oosample, fig=TRUE, echo=FALSE, width = 6.5>>=
# out of sample
set.seed(7)
par(mfrow = c(2,2))
qqrplot(pit_df_t, nsim = 100, main = "Distributional forest", ylim = c(-5,5), col = gray(0.1, alpha = 0.02), pch = 19)
qqrplot(pit_g_t, nsim = 100, main = "Prespecified GAM", ylim = c(-5,5), col = gray(0.1, alpha = 0.02), pch = 19)
qqrplot(pit_gb_t, nsim = 100, main = "Boosted GAM", ylim = c(-5,5), col = gray(0.1, alpha = 0.02), pch = 19)
qqrplot(pit_ml_t, nsim = 100, main = "EMOS", ylim = c(-5,5), col = gray(0.1, alpha = 0.02), pch = 19)

qqrplot(pit_ml_t, nsim = 100, main = "Boosted GAM", ylim = c(-5,5), col = gray(0.1, alpha = 0.02), pch = 19)
@
\caption{\label{qqr_oosample} Out-of-sample residual QQ-plots (2009--2012) for station Axams based on models learned on data from 1985--2008.}
\end{figure}

>>>>

\begin{figure}[t!]
\centering
\setkeys{Gin}{width=0.99\textwidth}
<<rain_axams_qqr_oosample, fig=TRUE, echo=FALSE, width = 6.5, pdf = FALSE, png = TRUE, resolution = 150>>=
# out of sample
set.seed(7)
par(mfrow = c(2,2))

qqrplot(pit_df_t, nsim = 100, main = "Distributional forest", ylim = c(-5,5), col = gray(0.04, alpha = 0.01), pch = 19)
qqrplot(pit_g_t, nsim = 100, main = "Prespecified GAM", ylim = c(-5,5), col = gray(0.04, alpha = 0.01), pch = 19)
qqrplot(pit_gb_t, nsim = 100, main = "Boosted GAM", ylim = c(-5,5), col = gray(0.04, alpha = 0.01), pch = 19)
qqrplot(pit_ml_t, nsim = 100, main = "EMOS", ylim = c(-5,5), col = gray(0.04, alpha = 0.01), pch = 19)
@
\caption{\label{qqr_oosample} Out-of-sample residual QQ-plots (2009--2012) for station Axams based on models learned on data from 1985--2008.}
\end{figure}
